Analysis of Physical Activity Survey(2022)

### 2022-04-27 outputs/paper/paper.Rmd
Model section finished

---
title: "Analysis of Physical Activity Survey(2022)"
author: 
  - Jonathan Goodwin
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Recreational activity and physical fitness are important factors in determining the health and safety of a society. We obtain data regarding the activity of individuals of different states and age groups as well as their respective distance to a park. We find that citizens who live closer to parks are more likely to be physically active, and that younger citizens are more likely to be physically active then older ones. These findings have implications for the future development of public recreational structures."
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
```{r setup, include=FALSE,warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message= FALSE, fig.pos = 'H')
library(tidyverse)
library(kableExtra)
library(reshape2)
```
```{r, echo = F}
### Reading CSV and setting seed###
set.seed(1)
Data <- 
  read.csv(here::here("outputs/data/cleaned_physical_activity.csv"))
```

@@

  We analyzed the sources of water for two subsets of the Jordan population, urban and rural residents. From Figure ###Reference### and Figure ###Reference###, we can see that both California is the state with the most active populace, and that New York is the state where residents most commonly walk and/or bike to work. We also see that more rural states like Nebraska and Alaska have the fewest people living near a park.

@@

@@

  The survey has been conducted every year for over 50 years, the sample is nationally representative, the intent of the survey is to monitor the health of the nation, as it collects information by interviewing American households. The content of the survey is updated roughly every 15-20 years with the most recent being in 2019. Of which 30,000 adults and 9,000 children were interviewed. Of this survey, this analysis focused on the information regarding the proportion of adults classified as obese or overweight, and how they responded to questions regarding aerobic activity and weight training. The data is collected from all 50 states including the District of Columbia and Peurto Rico, there is also a section included for the National averages of each question response.

@@

@@

```{r tab4, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means4 <- df_m[order(df_m$V4),]
names(df.means4)[names(df.means4) == 'V2'] <- 'State'
names(df.means4)[names(df.means4) == 'V4'] <- 'Proportion'
df.new4 <- cbind(df.means4$State,df.means4$Proportion)
knitr::kable(head(df.new4),booktabs = TRUE, align = "c", caption = "Excerpt of Chart 2") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

>>>>

---
title: "Analysis of Physical Activity Survey(2022)"
author: 
  - Jonathan Goodwin
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Recreational activity and physical fitness are important factors in determining the health and safety of a society. We obtain data regarding the activity of individuals of different states and age groups as well as their respective distance to a park. We find that citizens who live closer to parks are more likely to be physically active, and that younger citizens are more likely to be physically active then older ones. These findings have implications for the future development of public recreational structures."
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
```{r setup, include=FALSE,warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message= FALSE, fig.pos = 'H')
library(tidyverse)
library(kableExtra)
library(reshape2)
```
```{r, echo = F}
### Reading CSV and setting seed###
set.seed(1)
Data <- 
  read.csv(here::here("outputs/data/cleaned_physical_activity.csv"))
Data1 <- read.csv(here::here("outputs/data/cleaned_walk_or_bike.csv"))
```

@@

  We analyzed the sources of water for two subsets of the Jordan population, urban and rural residents. From Table \@ref(tab:tab2) and Table \@ref(tab:tab3), we can see that both Colorado is the state with the lowest rate of obesity and that Mississipi is the highest.

@@

  Overall we found that the state with the highest rates of Obesity was Mississipi, the lowest was Colorado and that there is a relationship between the proportion of state residents participating in recreational activities like muscle training or aerobics and the obesity rate of residents within that state.

@@

  The survey has been conducted every year for over 50 years, the sample is nationally representative, the intent of the survey is to monitor the health of the nation, as it collects information by interviewing American households. The content of the survey is updated roughly every 15-20 years with the most recent being in 2019. Of which 30,000 adults and 9,000 children were interviewed. Of this survey, this analysis focused on the information regarding the proportion of adults classified as obese or overweight, and how they responded to questions regarding aerobic activity and weight training. The data is collected from all 50 states including the District of Columbia, there is also a section included for the National averages of each question response.

@@

  The model being used is $\text{Obesity}=\beta_{\text{Intercept}}+\beta_{\text{150min of Aerobics}}\times (\text{150min of Aerobics or more})+\beta_{\text{Muscle Training}}\times (\text{Muscle Training})$. Where the beta coefficients represent the change in the predictor variables, 150min or more of Aerobics, and Muscle Training, have on the result, being the obesity rate. This model was chosen since other factors like no aerobic activity or 300min or more of aerobic activity were unsuprisingly highly correlated with the 150min of aerobics.

  Figure \@ref(fig:fig5) shows the relationship between 150min of Aerobics training and Muscle Training compared to the rate of Obesity.

```{r fig5, echo = FALSE, fig.cap = "Obesity vs 150min of Aerobics", fig.width=5,fig.height=5}
### Obesity Rate by State 2011 ###
df1 <- subset(df, Year == 2011)
df1 <- subset(df1, Question == "Percent of adults aged 18 years and older who have obesity")
df1 <- df1[order(df1$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df1[i,4],df1[i+1,4],df1[i+2,4],df1[i+3,4],df1[i+4,4],df1[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_means <- cbind(unique(df1$Year),unique(df1$State), unique(df1$Question), round(x, digits = 1))
df_means <- as.data.frame(df_means)

###### Forming dataframe for no aerobic activity

df_no_leisure <- subset(df, Year == 2011)
df_no_leisure <- subset(df_no_leisure, Question == "Percent of adults who engage in no leisure-time physical activity")
df_no_leisure <- df_no_leisure[order(df_no_leisure$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df_no_leisure[i,4],df_no_leisure[i+1,4],df_no_leisure[i+2,4],df_no_leisure[i+3,4],df_no_leisure[i+4,4],df_no_leisure[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_means_no <- cbind(unique(df_no_leisure$Year),unique(df_no_leisure$State), unique(df_no_leisure$Question), round(x, digits = 1))
df_means_no <- as.data.frame(df_means_no)

### Forming dataframe for >150min aerobic activity

df_150 <- subset(df, Year == 2011)
df_150 <- subset(df_150, Question == "Percent of adults who achieve at least 150 minutes a week of moderate-intensity aerobic physical activity or 75 minutes a week of vigorous-intensity aerobic activity (or an equivalent combination)")
df_150 <- df_150[order(df_150$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df_150[i,4],df_150[i+1,4],df_150[i+2,4],df_150[i+3,4],df_150[i+4,4],df_150[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_means_150 <- cbind(unique(df_150$Year),unique(df_150$State), unique(df_150$Question), round(x, digits = 1))
df_means_150 <- as.data.frame(df_means_150)
### Dataframe for muscle strengthening
df_muscle <- subset(df, Year == 2011)
df_muscle <- subset(df_muscle, Question == "Percent of adults who engage in muscle-strengthening activities on 2 or more days a week")
df_muscle <- df_muscle[order(df_muscle$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df_muscle[i,4],df_muscle[i+1,4],df_muscle[i+2,4],df_muscle[i+3,4],df_muscle[i+4,4],df_muscle[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_means_muscle <- cbind(unique(df_muscle$Year),unique(df_muscle$State), unique(df_muscle$Question), round(x, digits = 1))
df_means_muscle <- as.data.frame(df_means_muscle)

### Dataframe for >300min of aerobic activity

df_300 <- subset(df, Year == 2011)
df_300 <- subset(df_300, Question == "Percent of adults who achieve at least 300 minutes a week of moderate-intensity aerobic physical activity or 150 minutes a week of vigorous-intensity aerobic activity (or an equivalent combination)")
df_300 <- df_300[order(df_300$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df_300[i,4],df_300[i+1,4],df_300[i+2,4],df_300[i+3,4],df_300[i+4,4],df_300[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_means_300 <- cbind(unique(df_300$Year),unique(df_300$State), unique(df_300$Question), round(x, digits = 1))
df_means_300 <- as.data.frame(df_means_300)

### Linear Model

dat.m <- as.data.frame(cbind(df_means$V4,df_means_no$V4,df_means_300$V4,df_means_150$V4,df_means_muscle$V4))
names(dat.m)[names(dat.m) == 'V1'] <- "Obesity"
names(dat.m)[names(dat.m) == 'V2'] <- "No"
names(dat.m)[names(dat.m) == 'V3'] <- "300mins"
names(dat.m)[names(dat.m) == 'V4'] <- "150min"
names(dat.m)[names(dat.m) == 'V5'] <- "Muscle"
Obesity <- as.numeric(as.vector(dat.m$Obesity))
No_Aerobics <- as.numeric(as.vector(dat.m$No))
Aerobics_300min <- as.numeric(as.vector(dat.m$`300mins`))
Aerobics_150min <- as.numeric(as.vector(dat.m$`150min`))
Muscle <- as.numeric(as.vector(dat.m$Muscle))
mod1 <- lm(Obesity~Aerobics_150min+Muscle)
ggplot(mapping = aes(x = Aerobics_150min, y = Obesity))+geom_point()+xlab("150min or more of Aerobics") +
  ylab("Obesity Rate")
```

@@

```{r tab4, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means4 <- df_m[order(df_m$V4),]
names(df.means4)[names(df.means4) == 'V2'] <- 'State'
names(df.means4)[names(df.means4) == 'V4'] <- 'Proportion'
df.new4 <- cbind(df.means4$State,df.means4$Proportion)
knitr::kable(head(df.new4),booktabs = TRUE, align = "c", caption = "Excerpt of Figure 1") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```
